---
title: "20181022a Selector gadget and simple scraping"
author: "cheungngo"
date: "22 October 2018"
output: word_document
---

### Pre-requisites

```{r, message=FALSE}
library(rvest)
```

https://cran.r-project.org/web/packages/rvest/vignettes/selectorgadget.html  
Installing the selector gadget in chrome is also important to get the corresponding CSS selector from the desired fields in the webpage to be scraped.  

### Specifying the url and decode by read_html()

```{r}
url = 'https://www.ncbi.nlm.nih.gov/pubmed/?term=schizophrenia+memantine'
webpage = read_html(url)
webpage
```

### Using the CSS selctor (by the selectorgadget) to scrap the data by html_nodes() and html_text()

```{r}
# Suppose we are going to get the title  
# the CSS selector would be '.title' as shown by the selctor gadget
title_html = html_nodes(webpage, '.title')
head(title_html)
# convert the data to text
title = html_text(title_html)
head(title)
```

### Using gsub() to modify scraped data

```{r}
# scraping the authors of the studies
# '.desc' as detected by the selector
author_html = html_nodes(webpage,'.desc')
author = html_text(author_html)
head(author)
```

```{r}
# Suppose we only want the first author
author = gsub(',.*','',author)
author = as.factor(author)
head(author)
table(author)
```

### combining the data into a dataframe

```{r}
schiz_memantine_df = data.frame(Title = title, Author = author)
head(schiz_memantine_df)
```

